### 2020-06-30 related_work.tex
intro_cl_063016pm
related work

\section{Related Work}
\label{sec-related-work}
\begin{table*}[t]
    \caption{A comparison of state-of-the-art works on Wi-Fi Imaging.}
    \vspace{2mm}
    \begin{center}
    \begin{tabular}{ccccc}
    \hline
     Reference  & Principle &  RF Platform & Method & \#(Tx,Rx) Ant$^{\mathrm{a}}$\\ 
    \hline
    Wision~\cite{wision}  & Intensity & USRP-N210 & SAR & (1,8$\times$8)\\ 
    RF\_Avatar~\cite{rf_avatar}  & Intensity & FMCW Radio & DNN & (4,16)\\ 
    C. Karanam~\cite{3dimaging_uav} & Intensity (RSSI) & COTS Wi-Fi & SAR & (1,150$\times$150)$^{\mathrm{c}}$\\ 
    P. Proffitt~\cite{imaging_1} & Intensity & USRP-N210 & SAR \& DNN~\cite{MaskRCNN} & (180, 180)$^{\mathrm{b}}$\\ 
    P. Holl~\cite{holography} & Intensity \& Phase & 3D Hologram Simulation & Wave Front~\cite{angular} & (1,50$\times$40)$^{\mathrm{d}}$\\ 
    \hline
    \textbf{\textsf{WiHolo-2D}} & Intensity \& Polarization & COTS Wi-Fi & 2D IFFT \& GAN &(1,6) \\
    \hline
    \multicolumn{5}{l}{$^{\mathrm{a}}$Equivalent static antenna array for antenna scanning. $^{\mathrm{b}} $The receive beam sweeps from $+90^{\circ}$ to $-90^{\circ}$ for one}\\
    \multicolumn{5}{l}{transmit beam angle between $+90^{\circ}$ and $-90^{\circ}$. $^{\mathrm{c}}$The RX drone measures the RSSI every 2 cm for the 3m$\times$3m area.}\\
    \multicolumn{5}{l}{$^{\mathrm{d}}$Achieve a resolution of 4.0 cm $\times$ 7.2 cm for the 2m$\times$3m area.}\\
    \end{tabular}
    \label{comparison}
    \end{center}
\end{table*}

\cl{Compare existing work from several views to present advanntages of SRPeek. Keep the related work part within the page 3.}
\subsection{Shoulder Surfing}
With the arrival of the information era, privacy issues are becoming increasingly prominent. Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily in recent years. Surveys of shoulder surfing provides evidence of this behavior in real world \cite{eiband2017understanding} \cite{goucher2011look}, often more efficient than expected\cite{kwon2013covert}. Various techniques and systems have been designed to mitigate this threat. Some systems sense malicious passers-by and hide information \cite{brudy2014anyone} or warn the user\cite{saad2018communicating}; others modify the user interfaces to create honeypots (for passwords)\cite{chakraborty2014tag}, confuse unauthorized parties\cite{wiedenbeck2006design}, or making the interactions invisible\cite{kumar2007reducing} or unreadable from a distance\cite{Chun2019Keep}. Most of the works designing defenses against shoulder surfing assume that the attacker is a casual passer-by, taking occasional peeks with his/hers naked eye, as is the case most of the time\cite{eiband2017understanding}. However, it is the malicious ones, although few, that can utilize the information (passwords, business correspondence, etc.) they obtained to do real harm. On the other hand, the threat model of tool-assisted shoulder surfing is also studied. Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}. Maggi, et al. designed an automatic shoulder surfing threat model, observing the target smartphone with a camera\cite{maggi2011poster}, but without the help of SR techniques, this method can only function when the attacker is standing at close range, which is a barely practical scenario. With the development of smartphone camera, processing ability, and SR technology over the years, we propose a stronger shoulder surfing system in which attackers can successfully obtain information while keeping a distance to avoid suspicion, and prove that this threat is eminent in our daily life.

>>>>

\begin{table*}[t]
    \caption{A comparison of state-of-the-art works on shoulder surfing.}
    \vspace{2mm}
    \begin{center}
    \begin{tabular}{ccccc}
    \hline
     Reference & Subject & Range$^{\mathrm{a}}$ & Deployment & Performance\\ 
    \hline
    Wision~\cite{wision}  & Intensity & USRP-N210 & SAR & (1,8$\times$8)\\ 
    RF\_Avatar~\cite{rf_avatar}  & Intensity & FMCW Radio & DNN & (4,16)\\ 
    C. Karanam~\cite{3dimaging_uav} & Intensity (RSSI) & COTS Wi-Fi & SAR & (1,150$\times$150)$^{\mathrm{c}}$\\ 
    P. Proffitt~\cite{imaging_1} & Intensity & USRP-N210 & SAR \& DNN~\cite{MaskRCNN} & (180, 180)$^{\mathrm{b}}$\\ 
    P. Holl~\cite{holography} & Intensity \& Phase & 3D Hologram Simulation & Wave Front~\cite{angular} & (1,50$\times$40)$^{\mathrm{d}}$\\ 
    \hline
    \textbf{\textsf{SRPeek}} & Multi-type Characters & 1.5m \& 30$^\circ$ & COTS smartphones & Recovery 95\% Contents in Real Time \\
    \hline
    \multicolumn{5}{l}{$^{\mathrm{a}}$Equivalent static antenna array for antenna scanning.}\\
    \end{tabular}
    \label{comparison}
    \end{center}
\end{table*}

\section{Related Work}
\label{sec-related-work}

\cl{Compare existing work from several views to present advanntages of SRPeek. Keep the related work part within the page 3.}
\subsection{Shoulder Surfing}
With the arrival of the information era, privacy issues are becoming increasingly prominent. Smartphone screen privacy, the concern of our smartphones being observed by strangers in public areas, or shoulder surfing, have been studied heavily recently~\cite{eiband2017understanding,goucher2011look,kwon2013covert}. To mitigate this threat, some systems hide the information~\cite{brudy2014anyone} or warn the user~\cite{saad2018communicating} once sensing malicious passers-by; others modify the user interfaces, including creating honeypots (for passwords)~\cite{chakraborty2014tag}, confusing unauthorized parties~\cite{wiedenbeck2006design}, and making the interactions invisible~\cite{kumar2007reducing} or unreadable from a distance~\cite{Chun2019Keep}. Most of the works assume that the attacker is a casual passer-by, taking occasional peeks with the naked eye, as is the case most of the time~\cite{eiband2017understanding}. Given the assisted equipment, the malicious attacker can however acquire the sensitive information (passwords, business correspondence, etc.) readily to do real harm. To deal with the threat model of tool-assisted shoulder surfing\cl{more citations?},
% Schaub, et, al. observed the susceptibility of shoulder surfing from the naked eye\cite{schaub2012password}
Maggi et al. designed an automatic shoulder surfing threat model, observing the target smartphone with a camera\cite{maggi2011poster}. It can however only function when the attacker is standing at close range, which is a barely practical scenario. By tailoring and fusing the SR technology with smartphones with developed mobile camera module and processing ability, we propose a stronger shoulder surfing threat model in which attackers can successfully obtain information for a longer range to reduce suspicion. Evaluations demonstrate its feasibility and privacy concerns in our daily life.
